Growing Up with Nell: A Narrative Interface for Literacy

### 2012-03-12 paper.tex
Move Narcissus into a footnote to bring Bibliography back down to 1 column.

TurtleScript allows the child to dig as far into Nell's implementation
as their capabilities allow.  Although the operating system and the
browser implementation remain inaccessible, incorporating a
meta-circular interpreter for JavaScript (such as \cite{narcissus}) allows us
to expose the system all the way down to the programming
language implementation.
% Via TurtleScript, this code is all visible in a
% friendly block-based form.

>>>>

TurtleScript allows the child to dig as far into Nell's implementation
as their capabilities allow.  Although the operating system and the
browser implementation remain inaccessible, incorporating a
meta-circular interpreter for JavaScript%
\footnote{For example, \url{https://github.com/mozilla/narcissus/}}
% (such as \cite{narcissus})
allows us to expose the system all the way down to the programming
language implementation.
% Via TurtleScript, this code is all visible in a
% friendly block-based form.
